The necessity of hypermedia RDF and an approach to achieve it

### 2012-04-12 eswc-2012/workshop2.tex
Mention linked data basic profile
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@222 43ef1190-90fd-4dd7-a769-d0121f02b80e
trim a bit
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@223 43ef1190-90fd-4dd7-a769-d0121f02b80e

% TODO:
% POST in relation to graph store
% Weakness of RDF
% Reformulate something on SPARQL about enabling
% More writing around factors?

@@

The Atom Publishing Protocol\cite{atompub} is a widely cited as a good
example of a RESTful protocol and we note that it has a single service
endpoint. From there, you can navigate to what you need. This
motivates the first discussion topic of this paper:

@@

The second triple exists to make it possible to POST an RDF payload to
some URI and the server will itself assign a URI to the posted RDF
payload.

>>>>

% TODO:
% Reformulate something on SPARQL about enabling
% More writing around factors?

@@

We note that the Atom Publishing Protocol\cite{atompub} has a single
service endpoint. From there, you can navigate to what you need. This
motivates the first discussion topic of this paper:

@@

The second triple exists to make it possible to POST an RDF payload to
some URI and the server will itself assign a URI to the posted RDF
payload. This may for example be a named graph, as defined in
\cite{graphstore} or a follow the protocol recently suggested in
\cite{linkeddatabasicprofilesubmission}~Section~5.4.
